\documentclass[12pt, a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{nomencl}
\usepackage{makeidx}
\usepackage{setspace}

\makenomenclature
\title{{\Huge A Case study of \\ Interoperability in Health Information Systems \\ for Developing Countries} \\ Specialization Project, TDT4501, NTNU \\ Fall 2013 \\ {\small Supervisor: Eric Monteiro}}
\author{Student/Author: Kenneth Børtveit}
\begin{document}
\begin{onehalfspacing}
\maketitle
\tableofcontents
\listoffigures

\printnomenclature
%Compile, then run this command to make the nomenclature
%makeindex  filename.nlo -s nomencl.ist -o filename.nls
%Then compile a couple of times.
\begin{abstract}
This report gives an introduction to interoperability, transtion strategy and touches on the topic of ICT's in developing countries.
A case taking place at Rwandas Health Ministy is then presented.
Lastly some guides for how one could go from an interoperability issue to a descriptive plan in order to increase interoperability in an action based research process.
\end{abstract}
\chapter{Introduction}
This paper tries to describe how interoperability goes from being an issue to form an executeable plan in an environment with limited resources.
The paper partly based on action research.
Although the full iteration of the action research was not conducted, the diagnosis and planning were and will form the basis of a subsequent research.
The diagnosis was conducted as a exploratory case study at the Ministry of Health in Rwanda.
As a practitioner researcher I was able to collect qualitative data that would later form the basis for making the second step in the action research process.
This plan will define the steps that will be taken in order to decrease the presence of silos and increase interoperability in the health information systems of Rwanda.
By first introducing the relevant theory comparing this with the case study I will propose actions steps that would increase interoperability.
\input{litterature/litterature.tex} 
\input{empirical/empirical.tex}
\input{discussion/discussion.tex}
\input{bibliography.tex}
\input{appendix/appendix.tex}
\end{onehalfspacing}	
\end{document}