\part{Theory}
\chapter{Why worth the effort?}
\section{Internet access in the world}
In Africa, which
has a population of 700 million, fewer than one million
people had access to the internet in 1998, and of this
number 80\% were in South Africa. Among the other
20\% the ratio of people who have access to the internet
to those who do not is 1 to 5000, in the United States
or Europe the ratio is 1 to 6.5 \cite{11}
Here I want to explain why we look at this.
\chapter{F/OSS}
\section{The cathedral and the bazaar \cite{10}}
\section{The transformation of open source software \cite{3}}
\section{Licences}
\chapter{System Migration \cite{2} \cite{8}}
\section{Initiation}
Who is the initiators and how does this impact the choice of system.
\section{Implementation}
\subsection{What characterizes a successful implementation}
\section{Cut-Over}
\subsection{Evolutionary vs. Revolutionary}
\section{Migration Methods}
\subsection{The Big Bang}
\subsection{Forward Migration}
\subsection{Backwords Migration}
\subsection{The Chicken Little Strategy}
\subsection{The Butterfly Methodology}
\chapter{Health Information Systems}
\section{Women and access to the internet \cite{11}}
\section{Challanges in Exploiting IT \cite{4}}
\section{Description of health care work}
\section{Business Skills \cite{4}}
\section{What is the systems supposed to do?}
\section{Partnership between health personell and system developers}
\subsection{Translators between system developers and health personell \cite{9}}
\subsection{Something about Cognitive Overload(It is not called cognitive overload)}
\subsection{Information Systems That Helps(not a burden for the users)}
\section{Patient Care Information Systems}
\subsection{Health Care in Industrial Countries}
\subsubsection{Is this something to strive at?}
\subsubsection{System X}
\subsubsection{Sykehuspartner}
\subsection{Health Care in Developing Countries}
\subsection{F/OSS in Health Care}
\subsubsection{Trust issues}
\subsubsection{Customer support}
\subsubsection{Dependencies}
\chapter{Information Systems in Developing Countries \cite{7}}
\section{Why is it failing?}
\subsection{Is there anything in particular?}
\section{Sustainability}
