\section{Day 10}
\begin{tabular}{|c|c|}
\hline
Date: & 16.10.2013 \\
\hline
\end{tabular}
\subsection{Staff meeting}
We had a staff meeting today. Topics of the day was.
\begin{enumerate}
\item HMIS portal. Andrew got assigned to this. I really don't know what kind of portal this is. Maybe a website for the public?
\item Clean up DHIS2. Since everybody had recieved training in how to use the DHIS2 there been alot of analytics that has been made. This resulted in making browsing very unorganized. Gloria got the assignment of cleaning this up and making a naming convention.
\item New systems to the DHIS2.
	\begin{itemize}
	\item TRACNET. Dont know its purpose yet.
	\item CNLS. Dont know its purpose yet.
	\end{itemize}
\item Annual report. I was wondering what this report should contain. Are they using DHIS2 in order to make this?
\item NIKE foundation. I didn't mention this, but I think there should be some research about what they are doing since the guy at the `good house' was saying that they were doing alot of similiar things. My first idea was that we should share databases. But who knows, maybe there is some competition going on here.
\item SMS module. I really didn't get what this was really about. There is an easy way to do the dataentry in DHIS2, but there were some interest in the group of having an alert system based on some thresholds. I was thinking this should be done with an app.
\item DQA. This is an abbrevation for Data Quality Assesment. The main problem was that they would like to compare their data with samples from the field. DHIS2 does not support this functionality very well. This is a possible task. Something was mentioned about a report card that is being developed or been developed, but I didn't quite follow.
\item Then it was the Resource mapper. This relates to the overall architecture and the interoperateability thing. Gloria, Randy and Bob are working on this. 
\item The group is planning a training early this November. Should be thinking about growing a mustache. Anyways, the group is going to be trained in iReport and HTML report. Randy is putting this together.
\item We should upload some database files to the Gorilla server. Gesis HC and Gesis DH. Eventually putting them in the DatawareHouse.
\item At the end of the meeting it was mentioned that some of the members should think about their contracts. Are they looking for other jobs? Got me thinking about if they had secure jobs. What is their situation there?
\end{enumerate}

