\section{Day 1}
\begin{tabular}{|c|c|}
\hline
Date: & 07.10.2013 \\
\hline
\end{tabular}
\subsection{Traveling}
\subsubsection{Bus}
I started out with waking up at 05:00am. Usually I get my salary from Peppes at the 7th each month, but this time there was a delay.
So waking up, I was broke. No money for the Planebus. I tried to get some money from the local gas station with my mastercard with no luck.
With only 3minutes until my bus was leaving i hoped that the bus driver would accept my mastercard. He did.
Either way i was in luck, just before I was going to pay i checked my balance and my salary was in.
\subsubsection{Trondheim Airport}
No problem here. Talked a little with my mom, said goodbye and registrered. Plane ride was good.
\subsubsection{Oslo Airport}
Met up with Simen. There was some problems with he's visa. One cannot leave Norway and have a visa that expires before your return date.
He had fortunately bought a flex ticket so he could just change the dates, and then change them back when he arrives Kigali and prolonges his visa.
Then it was off to Istanbul. Flight was ok, good movies.
\subsubsection{Istanbul}
A little short on time. Didn't find the directions to our gate at first. The signs were properly hidden. After a little exploring we found it. Next stop, Kigali.
The flight seemed a little longer, but it was cured by `free cell' and `soduko'.
\subsubsection{Kigali}
At last, after about 18 hours from Trondheim, I was here. The guy that checked out our visa seemed a little sceptical, asked me one more time of my purpose of visit.
I just explained that we had an internship with the Management Sciences for Health and it was ok.
Felix picked us up and drove us to our house, 21KK Avenue, Niboye Road.
Awsome house! Randy's old place. We could stay here for free out October.
Took a beer with Felix and went to bed.
