\section{Day 2}
\begin{tabular}{|c|c|}
\hline
Date: & 08.10.2013 \\
\hline
\end{tabular}
\subsection{Meeting with Randy}
\subsubsection{Breakfast}
Got off to a bad start today. Woke up 10:05AM and we were expecting Randy at 10:00AM. No worries though, he wasn't there yet.
Took a shower. Simen sat outside talking to our day-time guard, Peter.
I took some breakfast, bread with jelly, a tomato and a banana. The bananas here are very small. Anyways, Randy came in the middle of breakfast and we talked some.
\subsubsection{Bank}
Then we drove out to the bank. About a 5 minute drive I think. We took out 100 000RFR, this should cover us for about 2 weeks Randy said. About 1000NOK.
Then we had to get our SIM-cards.
\subsubsection{MTN}
Pretty straight forward. We registreded our passports and got our sim cards with unlimitided data usage.
\subsubsection{Lunch}
We got liuch at a chiniese resturant. The food was not very great, but better than airplane food I think. Strong chilli. We got chicken, goat and some vegetables.
Simen and Randy were so kind and decided that for me.... 
We then got to talk about the project. In general I think we got 3 options.
Malarya registration by phone, system migration from Voxivia and a bigger project that involved several Systems and a Data warehouse.
The systems included HMS, Inidcator Remarks and health finances. The data warehouse should also be able to pull data from several instances.
We did not land on a specific one and we were presented with some other options as well.
The project that involved several instances had alot of subproject bound to it.
Andrew is the system wizard, Eric the doctor that likes his ways and Beth is a eager IT-person.
Randy talked a little about another survey that he thought was better than DHIS2. We should gather some recomendations here I think.
\subsubsection{The Office}
Then we went down to the office were we will probably work. Our space consists of 4 cubicals that we share with 2 others.
It was not far from the ministry of health.
\subsubsection{Back Home}
Randy had to go to a meeting so we called it a day. We were invited to join a training program on thursday later this week. Meeting up with Randy 08:30AM tomorrow.
