\section{Day 9}
\begin{tabular}{|c|c|}
\hline
Date: & 15.10.2013 \\
\hline
\end{tabular}
\subsection{Before lunch}
We've just had a solution. We first import the data that should be updated. Then we import data with the right zeros. We then select the records that should be updated and do so. NP I think..... I think the only troubling part is learning how to use SQL and the operating system. On thing should be mentioned before I forget. There is some efficency issues I think. I do think that it would be better if they learn a little more LINUX since they have the server.
\subsection{After lunch}
We have a solution for the database problem. We need to test it in order to be sure. Bah, lot of work. Anyways, this is important. So, moving on. We think we could implement the data entry report in DHIS2. This is fairly easy. We found a bug in the program. After creating the data elements and indicators and adding them to a dataset. We then bound them to an organisation unit, but the set would not show up. After deleting the set and re-insert them, DHIS2 would suddenly find them. Kinda important I think. That's about it.
\subsection{House hunting}
We've went to a couple of places for Simen's last days. I should probably look for a hotel or so for the last days here. I will tallk with Randy tomorrow. Scary shit the last place we were at. Simen did not think so much about it. The first place we went to was great though. Awsome, I would prefer to live there when I come back again after Christmas.

